A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging

### 2014-03-07 ECCV/paper.tex
Added new figures (with center), proof reading.

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{url}
\usepackage{comment}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\usepackage{multirow}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\captionsetup[table]{belowskip=12pt,aboveskip=4pt}
\setlength{\floatsep}{7pt plus 2pt minus 2pt}
\setlength{\textfloatsep}{7pt plus 2pt minus 2pt}
\setlength{\intextsep}{7pt plus 2pt minus 2pt}

@@

The recent availability of low-cost quadcopters has help to fuel significant efforts in
research focused on unmanned aerial vehicles.  Navigation and planning of
these vehicles is typically performed using onboard inertial sensors and/or
vision based modules that uses visual cues in the real world~(e.g.
\cite{Davison:2007,Engel12,Engel13}). However, to evaluate the effectiveness of
navigation methods, fiducial markers are commonly placed into the environment
to provide additional information that serves for ground-truth
positional measurements (e.g.,\cite{Bosnak:2012,Lim09,Klopschitz:2007}).

In order to be effective, fiducial markers (or simply, fiducials) need
to be easily detected in the scene.  A variety of fiducial markers
have been proposed in the literature
(e.g.,~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}).
These take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02,Fiala05})
or other geometric primitives arranged in predefined spatial patterns
(\cite{NaimarkF02,Pitag13,runetag11}).
Figure \ref{fig:teaser}-(a) show the popular ARTag\cite{Fiala05} as
seen from a quadcopter.  A problem for existing fiducials is that low-cost quadcopters
often exhibit very quick and erratic physical movements that
results in motion blur in the quadcopter's onboard camera.  This motion blur has
an adverse effect on the  recognition of fiducial  markers.  This can be seen in
Figure \ref{fig:teaser}-(b) where the ARTag cannot be recognized due to motion
blur. This is not too surprising as most  existing fiducials are not explicitly
designed to handle motion blur.

Compounding this problem is the additional issue of dropped video frames from
the quadcopter's wireless communication module.   This means that not only is blurring
introduced, but there may be large discontinuities in the patterns position due
to missing video frames.  As we will show in Section 4, this later problem
makes it challenging to apply tracking algorithms that can exploit temporal
coherence for determining the fiducial positions.

@@

\begin{figure}
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=\linewidth]{intersense.jpg}
  Intersense\cite{NaimarkF02}
 \end{subfigure}
 \begin{subfigure}[b]{0.14\textwidth}
 \centering
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}
 \end{subfigure}
 \begin{subfigure}[b]{0.14\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\cite{Fiala05}
 \end{subfigure}
 \begin{subfigure}[b]{0.14\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.jpg}
  Pi-Tag\cite{Pitag13}
 \end{subfigure}
 \begin{subfigure}[b]{0.14\textwidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{This figure shows the design of several existing fiducial markers.  While
 each codes have their own pros and cons of various environments, none are designed to be recognized under motion blur.}
 \label{fig:previous_work}
\end{figure}

\noindent{\textbf{Fiducials:}}~Figure~\ref{fig:previous_work} shows several
examples of existing fiducial markers.  Many designs use a two dimensional
barcode inside a rectangular grid. One examples of such a fiducial is from the 
ARToolkit~\cite{ARToolkit02}, a well known toolkit used in many augmented reality (AR) applications. Kato et al.\cite{kato-artoolkit} demonstrated the use of ARToolkit
to find the pose in video based AR conferencing system.

@@

There were also attempts to use circular patterns instead of rectangular. 
The use of concentric rings was used  by Gatrell et al.\cite{concentric}
for monocular pose estimation as well as object identification in space. Cho et al.
\cite{Cho:2001,Cho97fastcolor} have used multicolor rings instead of
black and white rings\cite{concentric} to increase possible number of fiducials.
These multicolor rings are used in wide area tracking in large scale
applications.  While based on a concentric rings, these particular approaches require 
the full ring to be recognized which is not possible when the pattern undergoes directional
motion blur.

Naimark et al.~\cite{NaimarkF02} proposed a circular bar code
called the, Circular Data Matrix that is beneficial in terms of
easy detection and ability to have a large number
of uniquely identifiable codes.  Addressing the issue of occlusion, 
Bergamasco et al. \cite{runetag11} proposed the RUNE-tag fiducial divided into number of
circular dots arranged them in circular fashion.
RUNE-tags can be detected even when up to 50\% of fiducial area is occluded.
Bergamasco et al.~\cite{Pitag13} proposed the Pi-Tag fiducial also composed 
of circular structures but arranged in a rectangle to exploit projective invariant cross-ration.
This provided similar occlusion resistance as RUNE-tag but with even less
circular dots. All of these techniques however relies on generic features
(e.g., circle detection) that break down under motion blur.

@@

Before we detail the design of our fiducial, we examine the performance of two
popular fiducials under motion blur.  Specifically we examine ARTags
\cite{Fiala05} and PiTags\cite{Pitag13} given their difference in geometry design.

To simulate the appearance of the maker as seen by a quadcopter,  we scaled down
the ARTag and PiTag fiducials to be size 150$\times$150 pixels. Both fiducials are then blurred
using linear motion blur at various orientations with different blurs scales.  
The blur motion ranged from 15 to 50 in magnitude (denoted in pixels),
representing small to significant motion blur. Figure \ref{fig:artag_pitag}
shows the visual appearance of the blurred tags.  We then try to detect the
markers using the ALVAR library~\cite{alvar} and Pi-Tag
library~\cite{ros_pitag}. The table in the left side of
Figure~\ref{fig:artag_pitag} shows the recognition rate (in percentage) of two
fiducial markers at various blur scales over all the different orientation.  
As we can see, the PiTag performance quickly diminished under small amounts of
blur, however, at 35 motion blur, ARTag is recognition rate drops to less than 20\%.

\noindent\begin{minipage}[h!]{\textwidth}
\noindent\begin{minipage}{0.6\textwidth}
\includegraphics[width=\textwidth]{artag_pitag.pdf}
%\captionof{figure}{Blurred AR Tag and Pi--tag with various blur scales}
\end{minipage}
\begin{minipage}{0.35\textwidth}
%\captionof{table}{Recognition rate of AR Tag and Pi-tag fiducial marker atvarious blur scales}
\begin{tabularx}{\textwidth}{|Y|Y|Y|}
\cline{1-3}
\small{Blur} & \multicolumn{2}{c|}{ \small{Recognition Rate}}
\\\cline{2-3}
\small{Scale}& \small{AR Tag} &	\small{Pi-Tag} \\ \cline{1-3}
\small{15} & \small{100} & \small{100} \\ %\cline{1-3}
\small{30} & \small{0} & \small{100} \\  %\cline{1-3}
\small{35} & \small{0} & \small{19} \\ %\cline{1-3}
\small{50} & \small{0} & \small{0} \\ \cline{1-3}
\end{tabularx}
\end{minipage}
\label{fig:artag_pitag}
\captionof{figure}{Figure showing ARTag and Pi-tag blurred with various blur
scales at different orientation. Table on the right shows the recognition rate
(in percent) of both fiducial markers at various blur scales along all blur
orientations.  Recognition rates for both tag is significantly reduced due to
blur. For severe blur, detection is not possible.}
\end{minipage}

@@

Figure \ref{fig:overall_flow} shows the process involved in fiducial
detection process. We give a brief overview of our algorithm here and details
to each step in the following.  Our detection algorithm has four steps. Step 1,
we apply a Gabor filter on the image captured through AR Drone to isolate the
potential locations of the pattern.  Step 2, we find the clusters of patches
found in Gabor output using spatial clustering.  Step 3, performs Principal
Component Analysis (PCA) on each cluster to find the dominate direction
unaffected by blur.  Step 4, based on the direction we extract the intensity
profile of the pattern and classify the code using a K-Nearest neighbor
classifier based on training data.

@@

\noindent Details of each of the steps are as follows:\\
\noindent\textbf{Gabor filter}: A 2D Gabor filter is a Gaussian kernel function
modulated by a sinusoidal plane wave~\cite{Kruizinga:2002}. It is used to find
high gradient patches from the image. In our case, it is used to detect blur
invariant sections of the fiducials. We have applied Gabor filter for eight
different orientations ($\theta = 0, 45, 90, \ldots ,225, 270, 315$).  The
following parameters where used for creating each Gabor kernel: $\lambda$ (wavelength) $= 8$, $\gamma$
(aspect ratio) $= 0.5$, $\sigma$ (spread) $= 0.56\lambda$, $\psi$
(phase angle) $= 0$ (for real part), $\pi/2$ (for imaginary part).
Then L2 norm of outputs along all orientations is calculated and finally L2
normalized image is thresholded with threshold set to $0.4$ (on scale of zero to
one).

@@

\noindent\textbf{Classification}: As mentioned above, a small image patch containing
the intensity profile of the fiducial is used to identify the code.   We found
that a training-based method using KNN gave better results than trying to directly determine
the number of transitions in the image patch.  To build the training-data, a
synthetic fiducial pattern is blurred along 36 orientations (0, 10, 20, \ldots
, 350) and its intensity profile along the first principal component from every
output is taken as training data for that fiducial pattern. Figure
\ref{fig:training_data} shows the process of creating this training data for
``01'' fiducial with.  For an input image patch, we normalize its intensity
range and then compare it against the training-data. The class label from the
closest top $K=5$ images in the training-data is used to label the patch.

@@

To increase the classification accuracy, training data for patterns having same
number of rings is grouped together; e.g., in two bit binary coded fiducial,
training data for pattern ``01'' and ``10'' will be grouped together, In three
bit binary coded fiducial, training data for pattern ``001'', ``010'' and
``100'' will form one group while training data for pattern ``110'', ``011'' and
``101'' will be in other group, etc. Now, depending on the number of detected
rings in test pattern, it is matched against corresponding group of training data, again
using  K-Nearest Neighbor Classifier. In this way, if we detect either zero
rings or maximum possible rings in the test pattern, there will be no need to do
further classification.

@@

\begin{figure}
\centering
  \includegraphics[width=.45\linewidth]{output_all_2.jpg}
  \includegraphics[width=.45\linewidth]{new_results/output_test_all1.jpg}
  \caption{Sample outputs containing all two bit binary coded fiducial patterns
  in single frame}
  \label{fig:output_all}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{blur_maximum.pdf}
\caption{Result of our fiducial detection algorithm on blur simulated data}
\label{fig:blur_maximum}
\end{figure}

The comparison of recognition rate is shown in Figure
\ref{fig:recognition_rate}. In this experiment, we use even more blur, up to 65
pixels.  The graph shows in Figure \ref{fig:recognition_rate} that our
recognition to 100\% for all codes except the ``00'' which has is undetectable
after 50 pixels blur (which is still significantly better than ARTag).  Reasons
for the ``00'' tags lower performance is discussed in Section~\ref{sec:discussion}.

@@

@@

We also compared results on the recorded feed using AR Drone quadcopter. In our
experimental setup, we have placed two AR Tags in the scene along with our fiducial  to
compare the resilience of blur by each fiducial type. We have used
ar\_track\_alvar, ROS Wrapper for ALVAR library \cite{ros_alvar}, to detect AR
Tags from the stream captured through quadcopter. In each test dataset, we used
different two bit binary coded fiducial and recorded video of around two minute
duration (i.e., around 1000 frames).   The quadcopter was flown in a routine
manner about the room with its camera facing the wall (see supplemental
videos). The comparison of recognition rate is shown in Table
\ref{tab:recongition_accuracy}. Classification accuracy of all fiducials (ARTag
as well as ours) ranges from 86.5\% to 94.1\%, while the AR Tag is 60.3\% to 65.6\%.
\begin{figure}
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.48\linewidth]{output_00.jpg}
  \includegraphics[width=0.48\linewidth]{new_results/output_00.jpg}
  \caption{Binary code ``00''}
  \label{fig:output0}
\end{subfigure}
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.48\linewidth]{output_01.jpg}
  \includegraphics[width=0.48\linewidth]{new_results/output_01.jpg}
  \caption{Binary code ``01''}
  \label{fig:output1}
\end{subfigure}
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.48\linewidth]{output_10.jpg}
  \includegraphics[width=0.48\linewidth]{new_results/output_10.jpg}
  \caption{Binary code ``10''}
  \label{fig:output2}
\end{subfigure}
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.48\linewidth]{output_11.jpg}
  \includegraphics[width=0.48\linewidth]{new_results/output_11.jpg}
  \caption{Binary code ``11''}
  \label{fig:output3}
  \end{subfigure}
  \caption{Sample outputs for two bit binary coded fiducials on different
  datasets. Class label attached to the detected fiducial is decimal equivalent
  of the binary code embedded in the detected fiducial.}
\end{figure}

@@

We also compare out approach with tracking designed for blurred input scenes. 
We have used four image sequences (consisting of around 1000 frames each), each
one containing a different blur resistent fiducial pattern to test the performance of
BLUT\cite{Wu:2011} and compare it with our result on the same image sequence.
From top rows of Figure \ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}. From
the images we can see that BLUT is able to track the fiducial when the position of
fiducial does not change too much in successive frames. Also, it can be seen
that, once BLUT looses the track of the fiducial, it is not able to recover. 
Since our approach detects the code at each frame, large changes in the patterns
position is not an issue.   Our detection results are also shown in Figure
\ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}.

@@

\noindent\textbf{False Negatives:}~~We found that sometimes our detection
algorithm fails to recognize our fiducial with binary code ``00'' when there is
large amount of blur.  When we
investigated the problem, we found that if there is too much blur the Gabor
output the innermost ring response it too low and not detected properly.  
This problem can be resolved by increasing radius of innermost ring to 
reduce the effect of blur on the innermost ring.

\noindent\textbf{Pose Estimation:}~~We note that other markers are able to give
full pose estimation after detection.  However, we are only able to reliably detect
the center point and therefore cannot estimate pose.  Of course, if four
markers were used in a known order pose could be estimated. The current
resolution of onboard camera will be main hurdle to clear before we can
effectively use multiple markers in each scene.

@@

Quadcopters are subject to quick and unstable motions that can cause significant
motion blur in the captured images. It severely affects the detection rate of
existing fiducial markers. We proposed the design of a fiducial that is robust
to motion blur. Our design of contrasting concentric rings is based on the the
observation that the direction perpendicular to the motion blur direction will
be unaffected by the blur and therefore still be recognizable. We have shown
through experimental validation that our fiducial will work under significant
amount of motion blur and can significantly out perform existing fiducial
markers under this scenario.

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
\usepackage{url}
\usepackage{comment}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
\usepackage{multirow}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\captionsetup[table]{belowskip=12pt,aboveskip=4pt}
\setlength{\floatsep}{7pt plus 2pt minus 2pt}
\setlength{\textfloatsep}{5pt plus 2pt minus 2pt}
\setlength{\intextsep}{7pt plus 2pt minus 2pt}

@@

The recent availability of low-cost quadcopters has helped to fuel significant
efforts in research focused on unmanned aerial vehicles.  Navigation and planning of
these vehicles is typically performed using onboard inertial sensors and/or
vision based modules that uses visual cues in the real world~(e.g., 
\cite{Davison:2007,Engel12,Engel13}). However, to evaluate the effectiveness of
navigation methods, fiducial markers are commonly placed into the environment
to provide additional information that serves for ground-truth
positional measurements (e.g.,\cite{Bosnak:2012,Lim09,Klopschitz:2007}).

In order to be effective, fiducial markers (or simply, fiducials) need
to be easily detected in the scene.  A variety of fiducial markers
have been proposed in the literature
(e.g.,~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}).
These take the form of binary codes arranged into rectangular grids (\cite{ARToolkit02,Fiala05})
or other geometric primitives arranged in predefined spatial patterns
(\cite{NaimarkF02,Pitag13,runetag11}).
Figure \ref{fig:teaser}-(a) shows the popular ARTag\cite{Fiala05} as
seen from a quadcopter.  A problem for existing fiducials is that low-cost quadcopters
often exhibit very quick and erratic physical movements that
results in motion blur in the quadcopter's onboard camera.  This motion blur has
an adverse effect on the  recognition of fiducial  markers.  This can be seen in
Figure \ref{fig:teaser}-(b) where the ARTag cannot be recognized due to motion
blur. This is not too surprising as most  existing fiducials are not explicitly
designed to handle motion blur.

Compounding this problem is the additional issue of dropped video frames from
the quadcopter's wireless communication module.   This means that not only is blurring
introduced, but there may be large discontinuities in the pattern's position due
to missing video frames.  As we will show in Section 4, this later problem
makes it challenging to apply tracking algorithms that can exploit temporal
coherence for determining the fiducial positions.

@@

\begin{figure}
\centering
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=0.8\linewidth]{intersense.jpg}
  Circular Data Matrix\cite{NaimarkF02}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\textwidth}
 \centering
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit\cite{ARToolkit02}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  AR Tag\quad\cite{Fiala05}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.jpg}
  Pi-Tag\quad\cite{Pitag13}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\textwidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{This figure shows the design of several existing fiducial markers.  While
 each code has their own pros and cons of various environments, none are
 designed to be recognized under motion blur.}
 \label{fig:previous_work}
\end{figure}

\noindent{\textbf{Fiducials:}}~Figure~\ref{fig:previous_work} shows several
examples of existing fiducial markers.  Many designs use a two dimensional
barcode inside a rectangular grid. One example of such a fiducial is from the 
ARToolkit~\cite{ARToolkit02}, a well known toolkit used in many augmented reality (AR) applications. Kato et al.\cite{kato-artoolkit} demonstrated the use of ARToolkit
to find the pose in video based AR conferencing system.

@@

There were also attempts to use circular patterns instead of rectangular. 
The use of concentric rings was done  by Gatrell et al.\cite{concentric}
for monocular pose estimation as well as object identification in space. Cho et al.
\cite{Cho:2001,Cho97fastcolor} have used multicolor rings instead of
black and white rings\cite{concentric} to increase possible number of fiducials.
These multicolor rings are used in wide area tracking in large scale
applications.  While based on a concentric rings, these particular approaches require 
the full ring to be recognized which is not possible when the pattern undergoes directional
motion blur.

Naimark et al.~\cite{NaimarkF02} proposed a circular bar code
called, the Circular Data Matrix that is beneficial in terms of
easy detection and ability to have a large number
of uniquely identifiable codes.  Addressing the issue of occlusion, 
Bergamasco et al. \cite{runetag11} proposed the RUNE-tag fiducial divided into number of
circular dots arranged in circular fashion.
RUNE-tags can be detected even when up to 50\% of fiducial area is occluded.
Bergamasco et al.~\cite{Pitag13} proposed the Pi-Tag fiducial, also composed 
of circular structures but arranged in a rectangle to exploit projective invariant cross-ratio.
This provided similar occlusion resistance as RUNE-tag but with even less
circular dots. All of these techniques however rely on generic features
(e.g., circle detection) that break down under motion blur.

@@

Before we detail the design of our fiducial, we examine the performance of two
popular fiducials under motion blur.  Specifically we examine  ARTags
\cite{Fiala05} and PiTags\cite{Pitag13} given their difference in geometry design.
We didn't find source code as well as samples for RUNE-tag\cite{runetag11}
online. Also, for Circular data matrix\cite{NaimarkF02}, the software should be
used with their proprietary hardware. So, we couldn't examine these fiducials.

To simulate the appearance of the maker as seen by a quadcopter,  we scaled down
the ARTag and PiTag fiducials to be size 150$\times$150 pixels. Both fiducials are then blurred
using linear motion blur at various orientations with different blurs scales.  
The blur motion ranged from 15 to 50 in magnitude (denoted in pixels),
representing small to significant motion blur. Figure \ref{fig:artag_pitag}
shows the visual appearance of the blurred tags.  We then try to detect the
markers using the ALVAR library~\cite{alvar} and Pi-Tag
library~\cite{ros_pitag}. The table in the left side of
Figure~\ref{fig:artag_pitag} shows the recognition rate (in percentage) of two
fiducial markers at various blur scales over all the different orientations.  
As we can see, the PiTag performance quickly diminished under small amounts of
blur, however, at 35 motion blur, ARTag's recognition rate drops to less than
20\%.

\noindent\begin{minipage}[h!]{\textwidth}
\noindent\begin{minipage}{0.6\textwidth}
\includegraphics[width=\textwidth]{artag_pitag.pdf}
%\captionof{figure}{Blurred AR Tag and Pi--tag with various blur scales}
\end{minipage}
\begin{minipage}{0.35\textwidth}
%\captionof{table}{Recognition rate of AR Tag and Pi-tag fiducial marker atvarious blur scales}
\begin{tabularx}{\textwidth}{|Y|Y|Y|}
\cline{1-3}
\small{Blur} & \multicolumn{2}{c|}{ \small{Recognition Rate}}
\\\cline{2-3}
\small{Scale}& \small{AR Tag} &	\small{Pi-Tag} \\ \cline{1-3}
\small{15} & \small{100} & \small{100} \\ %\cline{1-3}
\small{30} & \small{0} & \small{100} \\  %\cline{1-3}
\small{35} & \small{0} & \small{19} \\ %\cline{1-3}
\small{50} & \small{0} & \small{0} \\ \cline{1-3}
\end{tabularx}
\end{minipage}
\label{fig:artag_pitag}
\captionof{figure}{Figure showing ARTag and Pi-tag blurred with various blur
scales at different orientations. Table on the right shows the recognition rate
(in percent) of both fiducial markers at various blur scales along all blur
orientations.  Recognition rates for both tag is significantly reduced due to
blur. For severe blur, detection is not possible.}
\end{minipage}

@@

Figure \ref{fig:overall_flow} shows the process involved in fiducial
detection. We give a brief overview of our algorithm here and details
to each step in the following.  Our detection algorithm has four steps. Step 1,
we apply a Gabor filter on the image captured through AR Drone to isolate the
potential locations of the pattern.  Step 2, we find the clusters of patches
found in Gabor output using spatial clustering.  Step 3, performs Principal
Component Analysis (PCA) on each cluster to find the dominant direction
unaffected by blur.  Step 4, based on the direction we extract the intensity
profile of the pattern and classify the code using a K-Nearest neighbor
classifier based on training data.

@@

\noindent Details of each of the steps are as follows:\\
\noindent\textbf{Gabor filter}: A 2D Gabor filter is a Gaussian kernel function
modulated by a sinusoidal plane wave~\cite{Kruizinga:2002}. It is used to find
high gradient patches from the image. In our case, it is used to detect blur
invariant sections of the fiducials. We have applied Gabor filter for eight
different orientations ($\theta = 0, 45, 90, \ldots ,225, 270, 315$).  The
following parameters were used for creating each Gabor kernel: $\lambda$ (wavelength) $= 8$, $\gamma$
(aspect ratio) $= 0.5$, $\sigma$ (spread) $= 0.56\lambda$, $\psi$
(phase angle) $= 0$ (for real part), $\pi/2$ (for imaginary part).
Then L2 norm of outputs along all orientations is calculated and finally L2
normalized image is thresholded with threshold set to $0.4$ (on scale of zero to
one).

@@

\noindent\textbf{Classification}: As mentioned above, a small image patch containing
the intensity profile of the fiducial is used to identify the code.   We found
that a training-based method using KNN gave better results than trying to
find binary code directly by determining the presence (or absence) of ring
 at particular positions in the image patch. To build
 the training-data, a synthetic fiducial pattern is blurred along 36 orientations (0, 10, 20, \ldots , 350) with blur scale set to 40, and its intensity profile along the first principal component from every output is
taken as training data for that fiducial pattern. Figure
\ref{fig:training_data} shows the process of creating training data for
fiducial with binary code ``01'' embedded in it.  For an input image patch, we
normalize its intensity range and then compare it against the training-data.
The class label from the closest top $K=5$ images in the training-data is used
to label the patch.

@@

We are able to find the number of rings in the fiducial by finding transitions
in the intensity profile. To increase the classification accuracy, training data
for patterns having same number of rings is grouped together; e.g., in two bit
binary coded fiducial, training data for pattern ``01'' and ``10'' will be
grouped together, In three bit binary coded fiducial, training data for pattern
``001'', ``010'' and ``100'' will form one group while training data for
pattern ``110'', ``011'' and ``101'' will be in other group, etc. Now,
depending on the number of detected rings in test pattern, it is matched
against corresponding group of training data, again using  K-Nearest Neighbor
Classifier. In this way, if we detect either zero rings or maximum possible
rings in the test pattern, there will be no need to do further classification.

@@

\begin{figure}[ht!]
\centering
  \includegraphics[width=.45\linewidth]{output_all_2.jpg}
  \includegraphics[width=.45\linewidth]{new_results/output_test_all1.jpg}
  \caption{Sample outputs containing all two bit binary coded fiducial patterns
  in single frame}
  \label{fig:output_all}
\end{figure}

@@

The comparison of recognition rate is shown in Figure
\ref{fig:recognition_rate}. In this experiment, we use even more blur, up to 65
pixels.  The graph shows in Figure \ref{fig:recognition_rate} that our
recognition is 100\% for all codes except the ``00'' which is undetectable
after 50 pixels blur (which is still significantly better than ARTag).  Reasons
for the ``00'' tags lower performance is discussed in Section~\ref{sec:discussion}.

@@

\begin{figure}
\includegraphics[width=\linewidth]{blur_maximum.pdf}
\caption{Result of our fiducial detection algorithm on blur simulated data.
Detection result is shown on each of our fiducial pattern, blurred at the
maximum scale it can handle.}
\label{fig:blur_maximum}
\end{figure}

@@

We also compared results on the recorded feed using AR Drone quadcopter. In our
experimental setup, we have placed two AR Tags in the scene along with our fiducial  to
compare the resilience of blur by each fiducial type. We have used
ar\_track\_alvar, ROS Wrapper for ALVAR library \cite{ros_alvar}, to detect AR
Tags from the stream captured through quadcopter. In each test dataset, we used
different two bit binary coded fiducial and recorded video of around two minute
duration (i.e., around 1000 frames).   The quadcopter was flown in a routine
manner in the room with its camera facing the wall (see supplemental
videos). The comparison of recognition rate is shown in Table
\ref{tab:recongition_accuracy}. Recognition rate of our fiducials ranges from
86.5\% to 94.1\%, while the AR Tag is 60.3\% to 65.6\%. Classification
accuracy of all fiducials (ARTag as well as ours) was approximately 100\%.

\begin{figure}[hb!]
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.48\linewidth]{output_00.jpg}
  \includegraphics[width=0.48\linewidth]{new_results/output_00.jpg}
  \caption{Binary code ``00''}
  \label{fig:output0}
\end{subfigure}
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.48\linewidth]{output_01.jpg}
  \includegraphics[width=0.48\linewidth]{new_results/output_01.jpg}
  \caption{Binary code ``01''}
  \label{fig:output1}
\end{subfigure}
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.48\linewidth]{output_10.jpg}
  \includegraphics[width=0.48\linewidth]{new_results/output_10.jpg}
  \caption{Binary code ``10''}
  \label{fig:output2}
\end{subfigure}
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.48\linewidth]{output_11.jpg}
  \includegraphics[width=0.48\linewidth]{new_results/output_11.jpg}
  \caption{Binary code ``11''}
  \label{fig:output3}
  \end{subfigure}
  \caption{Sample outputs for two bit binary coded fiducials on different
  datasets. Class label attached to the detected fiducial is decimal equivalent
  of the binary code embedded in the detected fiducial.}
\end{figure}

@@

We also compare out approach with tracking designed for blurred input scenes. 
We have used four image sequences (consisting of around 1000 frames each), each
one containing a different blur resistant fiducial pattern to test the performance of
BLUT\cite{Wu:2011} and compare it with our result on the same image sequence.
From the images in top rows of Figure
\ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}, we can see that BLUT is able to track the fiducial when the position of fiducial does not change too much in successive frames. Also, it can be seen that, once BLUT looses the track of the fiducial, it is not able to recover. 
Since our approach detects the code at each frame, large changes in the patterns
position is not an issue.   Our detection results are also shown in Figure
\ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}.

@@

\noindent\textbf{False Negatives:}~~We found that sometimes our detection
algorithm fails to recognize our fiducial with binary code ``00'' when there is
large amount of blur.  When we
investigated the problem, we found that if there is too much blur, the innermost
ring's response in the Gabor output is too low and not detected properly.  
This problem can be resolved by increasing radius of innermost ring to 
reduce the effect of blur on the innermost ring.

\noindent\textbf{Pose Estimation:}~~We note that other markers are able to give
full pose estimation after detection.  However, we are only able to reliably detect
the center point and therefore cannot estimate pose.  Of course, if four
markers were used in a known order, pose could be estimated. The current
resolution of onboard camera will be main hurdle to clear before we can
effectively use multiple markers in each scene.

@@

Quadcopters are subject to quick and unstable motions that can cause significant
motion blur in the captured images. It severely affects the detection rate of
existing fiducial markers. We proposed the design of a fiducial that is robust
to motion blur. Our design of contrasting concentric rings is based on the 
observation that the direction perpendicular to the motion blur direction will
be unaffected by the blur and therefore still be recognizable. We have shown
through experimental validation that our fiducial will work under significant
amount of motion blur and can significantly outperform existing fiducial
markers under this scenario.
